---
title: "Assignment B1"
author: "Cathy Yan"
date: "2022-10-31"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(testthat)
```

## Tasks 1 and 2

```{r}
#' Identify the most frequently occurring item
#' 
#' This function calculates the frequency of occurrence of each factor level within a column of a data frame and returns the level that occurs most frequently.
#' 
#' @param df a dataframe with at least one column that's a factor; named after the common abbreviation for dataframe
#' @param factor the name of the column that is the factor to be counted; named for its data type
#' 
#' @return returns the name of the most frequently occurring factor level. If there is a tie, it returns both (or more) of the factor levels. 

most_frequent <- function(df, factor){
  stopifnot(is.factor(df[,factor]))
  
  tallied <- df %>%
    group_by_at(all_of(factor)) %>%
    summarize(count = n()) %>%
    filter(count == max(count)) %>%
    select(factor) %>%
    pull() %>%
    as.character()
  
  output <- tallied
  return(output)
}
```

## Task 3

Using the `fish_encounters` dataset, I can output the most prolific stations:

```{r}
fish_encounters <- as.data.frame(fish_encounters)
fish_encounters$station <- as.factor(fish_encounters$station)

most_frequent_station <- most_frequent(fish_encounters, "station")

print(levels(fish_encounters$station)) # all stations
print(most_frequent_station) # most prolific stations
```

Using the `iris` dataset, where all three species occur at the same frequency:

```{r}
most_frequent_iris <- most_frequent(iris, "Species")
print(most_frequent_iris)
```

Using the `mtcars` dataset, I can demonstrate that the function does not work if the data type is not a factor:

```{r, error = TRUE}
most_frequent_disp <- most_frequent(mtcars, "disp")
```

## Task 4

I will create a small dataset to test how my function performs when:

1. There is one item that occurs most frequently
2. All items occur in equal frequencies
3. The column is not a factor

```{r}
sample_df <- data.frame("cake" = c("red velvet", "red velvet", "vanilla", "chocolate", "red velvet", "red velvet"),
                        "client" = c("client 1", "client 1", "client 2", "client 2", "client 3", "client 3"),
                        "cost" = c(12, 12, 14.50, 10.25, 12, 12))
sample_df$cake <- as.factor(sample_df$cake)
sample_df$client <- as.factor(sample_df$client)

tests <- test_that("Testing frequency function", {
  expect_equal(most_frequent(sample_df, "cake"), "red velvet")
  expect_equal(most_frequent(sample_df, "client"), c("client 1", "client 2", "client 3"))
  expect_error(most_frequent(sample_df, "cost"), "is.factor(df[, factor]) is not TRUE", fixed = T)
})
```



